%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Mercedes-Benz}{Aug 2024 -- Present}
    {AI Research - Working Student $\cdot$ part-time}{Böblingen, Germany}
    \resumeItemListStart
        \resumeItem{Focusing on Neuromorphic computing.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Artpark, Indian Institute of Science}{Jul 2023 -- Oct 2023}
    {Machine Learning Engineer Consultant $\cdot$ part-time}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Built a prototype using RAGs (retrieval augmented generation) on LLMs to improve knowledge dissemination to Auxiliary Nursing Midwifery to help in quicker help with pregnancy care on the field.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Rephrase AI \normalfont{\scriptsize{(acquired by \textbf{\footnotesize{Adobe}})}}}{Apr 2022 -- Jun 2023}
    {Deep Learning Researcher $\cdot$ full-time}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Used Variational Auto-encoders (VAEs) and Generative Adversarial Networks (GANs) to work on generative speech, creating a proof of concept for voice cloning with few seconds of target speaker's voice samples.}
        \resumeItem{Used off-the-self speech content encoders (hubert-soft) to flag problematic speech on production systems. Further, my explorations in speech encoders helped us improve our lip-sync model.}
        \resumeItem{Improved team's experimental throughput by integrating ML experimenting frameworks like pytorch-lightning.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Wadhwani AI \normalfont{\scriptsize{(non-profit funded by the \textbf{\footnotesize{Gates Foundation}})}}}{Jun 2020 -- Mar 2022}
    {Associate ML Scientist I $\cdot$ full-time}{Mumbai, India}
    \resumeItemListStart
        \resumeItem{Led the development of a \href{https://www.wadhwaniai.org/2021/03/15/giving-lpa-a-hand/}{\underline{research prototype}} for scanning and interpreting medical docs using template matching and classical computer vision.}
        \resumeItem{For our mobile solution, implemented and deployed SOTA Deep Learning techniques for object detection.}
        \resumeItem{Experimented with sample rejection of adversarial inputs in the wild. \textbf{(NeurIPS 2022 workshop, ICLR 2023)}}
        \resumeItem{Coauthored a \href{https://www.idhsustainabletrade.com/uploaded/2021/05/WIAI-IDH-DD-AI-holds-water-white-paper-May-2021.pdf}{\underline{white paper}} detailing potential venues for AI disruption in Indian agriculture.}
        \resumeItem{Represented Wadhwani AI at Google's \textit{AI for Agriculture Hackathon} and won a cash reward of 1 million rupees.}
    \resumeItemListEnd

    \resumeSubheading
    {IIT Gandhinagar}{May 2019 -- Jul 2019}
    {Summer Research Intern}{Gandhinagar, India}
    \resumeItemListStart
        \resumeItem{Authored an \href{https://distill.pub/2020/bayesian-optimization}{\underline{expository article}} on Bayesian Optimization. \textbf{(Distill 2020)}}
        \resumeItem{Created Polire and Vayu for aiding research in computational sustainability. \textbf{(Poster at SenSys 2020).}}
        \resumeItem{Used active learning for optimal sensor placement recommendation to reduce costs. \textbf{(CoDS COMAD 2020, ICML Workshop 2020.}}
    \resumeItemListEnd

    \resumeSubheading
    {NVIDIA}{May 2018 -- Aug 2018}
    {Accelerated HPC \& Machine Learning Intern}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Implemented GPU-optimized Kalman filters in \href{https://github.com/rapidsai/cusignal/}{\underline{rapids.ai}}, a data science framework utilizing NVIDIA GPUs.}
        \resumeItem{Created a library to generate multivariate Gaussian random numbers on GPU using a standard normal sampler.}
    \resumeItemListEnd


\resumeSubHeadingListEnd